---
title: "Data exploration"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
    self_contained: true
---



```{r include=FALSE}

library(tidyverse)
library(labelled)
library(knitr)
library(visdat)
library(scales)
library(kableExtra)
theme_set(theme_bw())

```

```{r include=FALSE}
d <- read_rds("../../Data/01_preprocessed.rds")
```
## Variable overview

```{r}
glimpse(d)
```
```{r}
d %>% summary()
```


## Life satisfaction
```{r}
d2 <- d %>% 
  select(Zufriedenheit_allgLeben) %>% 
    group_by(Zufriedenheit_allgLeben) %>% 
  tally() 
```

```{r}
  ggplot(d2, aes(x = Zufriedenheit_allgLeben, y = n, label = n)) + 
  geom_bar(stat = "identity") + 
  geom_label(position = position_stack(vjust = 0.5)) + 
  coord_flip() + 
  labs(x ="Life satisfaction (0 = very low, 10 = very high)", y = "n")
```

## Study regions

```{r}
d2 <- d %>% 
  select(Meta_Studienregion) %>% 
  group_by(Meta_Studienregion) %>% 
  tally(); d2
```

```{r}
ggplot(d2, aes(x = Meta_Studienregion, y = n, label = n)) +
  geom_bar(stat = "identity") + 
  geom_label(position = position_stack(vjust = 0.5))+ 
  coord_flip()
```


## Age

```{r}
ggplot(d, aes(x = Person_Alter)) + 
  geom_histogram(binwidth = 1)
```

```{r}
d %>% select(Person_Alter) %>% summary()
```


## Gender

```{r}
d2 <- d %>% 
  select(Person_Gender) %>% 
  group_by(Person_Gender) %>% 
  tally() %>%
  filter(!is.na(Person_Gender)) %>% 
  mutate(shr = percent(n / sum(n))); d2
```

```{r}
ggplot(d2, aes(x = Person_Gender, y = n, label = shr)) + 
  geom_bar(stat = "identity") + 
  geom_label(position = position_stack(vjust = 0.5)) +
  coord_flip()
```



## Residence security

```{r}
d2 <- d %>% 
  select(Person_Aufenhaltssicherheit) %>% 
  group_by(Person_Aufenhaltssicherheit) %>% 
  tally() %>%
  filter(!is.na(Person_Aufenhaltssicherheit)) %>% 
  mutate(shr = percent(n / sum(n))); d2
```

```{r}
ggplot(d2, aes(x = Person_Aufenhaltssicherheit, y = n, label = shr)) + 
  geom_bar(stat = "identity") + 
  geom_label(position = position_stack(vjust = 0.5)) + 
  coord_flip()
```


## Children

```{r}
d2 <- d %>% 
  select(Person_Kinder) %>% 
  group_by(Person_Kinder) %>% 
  tally() %>%
  filter(!is.na(Person_Kinder)) %>% 
  mutate(shr = percent(n / sum(n))); d2
```

```{r}
ggplot(d2, aes(x = Person_Kinder, y = n, label = shr)) + 
  geom_bar(stat = "identity") + 
  geom_label(position = position_stack(vjust = 0.5)) + 
  coord_flip()
```

## Single houshold


```{r}
d2 <- d %>% 
  select(Person_Einzelhaushalt ) %>% 
  group_by(Person_Einzelhaushalt ) %>% 
  tally() %>%
  filter(!is.na(Person_Einzelhaushalt )) %>% 
  mutate(shr = percent(n / sum(n))); d2
```

```{r}
ggplot(d2, aes(x = Person_Einzelhaushalt , y = n, label = shr)) + 
  geom_bar(stat = "identity") + 
  geom_label(position = position_stack(vjust = 0.5)) + 
  coord_flip()
```


## Educational level

```{r}
d2 <- d %>% 
  select(Person_BildAbschluss ) %>% 
  group_by(Person_BildAbschluss ) %>% 
  tally() %>%
  filter(!is.na(Person_BildAbschluss )) %>% 
  mutate(shr = percent(n / sum(n))); d2
```

```{r}
ggplot(d2, aes(x = Person_BildAbschluss , y = n, label = shr)) + 
  geom_bar(stat = "identity") + 
  geom_label(position = position_stack(vjust = 0.5)) + 
  coord_flip()
```



```{r}
d2 <- d %>% 
  select(Person_persEinkommen ) %>% 
  group_by(Person_persEinkommen ) %>% 
  tally() %>%
  filter(!is.na(Person_persEinkommen )) %>% 
  mutate(shr = percent(n / sum(n))); d2
```

```{r}
d$Person_persEinkommen %>% summary()
```

```{r}
ggplot(d, aes(x = Person_persEinkommen)) + 
  geom_histogram(binwidth = 1500)
```

## Work sector

```{r}

```{r}
d2 <- d %>% 
  select(Person_Einzelhaushalt ) %>% 
  group_by(Person_Einzelhaushalt ) %>% 
  tally() %>%
  filter(!is.na(Person_Einzelhaushalt )) %>% 
  mutate(shr = percent(n / sum(n))); d2
```

```{r}
ggplot(d2, aes(x = Person_Einzelhaushalt , y = n, label = shr)) + 
  geom_bar(stat = "identity") + 
  geom_label(position = position_stack(vjust = 0.5)) + 
  coord_flip()
```


## Educational level

```{r}
d2 <- d %>% 
  select(Person_Taetigkeitsbereich ) %>% 
  group_by(Person_Taetigkeitsbereich ) %>% 
  tally() %>%
  filter(!is.na(Person_Taetigkeitsbereich )) %>% 
  mutate(shr = percent(n / sum(n))); d2
```

```{r}
ggplot(d2, aes(x = Person_Taetigkeitsbereich , y = n, label = shr)) + 
  geom_bar(stat = "identity") + 
  geom_text(position = position_stack(vjust = 0.5)) + 
  coord_flip()
```
```






