---
title: "Descriptive overview"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
    self_contained: true
---


```{r include=FALSE}

library(tidyverse)
library(labelled)
library(knitr)
library(visdat)
library(scales)
library(kableExtra)
library(Hmisc)
library(corrplot)
theme_set(theme_bw())
options(scipen = 99999)

```

```{r include=FALSE}
d <- read_rds("../../Data/01_preprocessed.rds")
```



# Group comparisons

##  Case study areas

Is there a significant difference between life satisfaction of people living within or outside a nature park?


```{r}

d1 <- d %>% 
  select(Meta_Studienregion, Zufriedenheit_allgLeben) %>% 
  transmute(
    Region = ifelse(test = Meta_Studienregion == "Kontrollregion", yes = "Kontrollregion", no = "Naturpark"), 
    Zufriedenheit_allgLeben); d1

d1 %>% 
  group_by(Region) %>% 
  summarise(meanZufried = mean(Zufriedenheit_allgLeben, na.rm = T), 
            sdZufried = sd(Zufriedenheit_allgLeben, na.rm = T), 
            n = n())

ggplot(d1, aes(x = Zufriedenheit_allgLeben)) + 
  facet_grid(Region ~ .) +
  geom_histogram(binwidth = 1)


```


## Normality

The histogramm show quite clearly that the data is not distributed normally. 
Nevertheless, I try out a test for normality
https://towardsdatascience.com/6-ways-to-test-for-a-normal-distribution-which-one-to-use-9dcf47d8fa93


```{r}
ggplot(d, aes(sample = Zufriedenheit_allgLeben)) +
  stat_qq() + 
  stat_qq_line()
```


```{r}
shapiro.test(d$Zufriedenheit_allgLeben)
```

The null hypothesis of these tests is that “sample distribution is normal”. If the test is significant, the distribution is non-normal. So if the P value is less than 0.05, you reject the null hypothesis and do not assume a normal distribution. 

So, this confirms our previous conclusion that the data is not normaly distributed.


## Comparing regions

```{r}
res <- wilcox.test(Zufriedenheit_allgLeben ~ Region, 
                   data = d1, 
                   exact = FALSE)
res
```

With a p value of 0.2735, we cannot reject the 0 hypothesis (that both populations are identical). In other word, there is no significant difference between the Kontroll Regions and the Nature Parks.


## Comparing sex

```{r}
d %>% 
  select(Person_Gender, Zufriedenheit_allgLeben) %>% 
  group_by(Person_Gender) %>% 
  summarise(meanZufried = mean(Zufriedenheit_allgLeben, na.rm = T), 
            sdZufried = sd(Zufriedenheit_allgLeben, na.rm = T), 
            n = n())

res <- wilcox.test(Zufriedenheit_allgLeben ~ Person_Gender, 
                   data = d, 
                   exact = FALSE);  res

```

Here we have a p value of 0.03555. As this is below the significance level of 0.05 we can conclude the there is a significan difference between women and men. 


## Comparing parenthood 

```{r}
d %>% 
  group_by(Person_Kinder) %>% 
  summarise(meanZufried = mean(Zufriedenheit_allgLeben, na.rm = T), 
            sdZufried = sd(Zufriedenheit_allgLeben, na.rm = T), 
            n = n())

res <- wilcox.test(Zufriedenheit_allgLeben ~ Person_Kinder, 
                   data = d, 
                   exact = FALSE); res

```
As the p-value is is below the significance level of 0.05 we can conclude the there is a significan difference between parents and non parents. 


```{r}


d %>%
  group_by(Person_Aufenhaltssicherheit) %>%
  summarise(meanZufried = mean(Zufriedenheit_allgLeben, na.rm = T),
            sdZufried = sd(Zufriedenheit_allgLeben, na.rm = T),
            n = n())

ggplot(d, aes(x = Person_Aufenhaltssicherheit, Zufriedenheit_allgLeben)) +
  geom_boxplot()
  


```


## Age and life satisfaction


```{r}

table(d$Zufriedenheit_allgLeben, d$Person_Alter)

d1 <- d %>%
  select(Zufriedenheit_allgLeben, Person_Alter) %>%
  group_by(Person_Alter) %>%
  summarise(zMean = mean(Zufriedenheit_allgLeben, na.rm = T),
            n = n()); d1

ggplot(d1, aes(x = Person_Alter, y = zMean)) +
  geom_bar(stat = "identity")

d2 <- d %>%
  select(Zufriedenheit_allgLeben, Person_Alter) %>% 
  group_by(Zufriedenheit_allgLeben, Person_Alter) %>% 
  tally(); d2

ggplot(d2, aes(x = Person_Alter, y = Zufriedenheit_allgLeben)) + 
  geom_point(aes(size = n))

rcorr(d$Zufriedenheit_allgLeben, d$Person_Alter)



```



```{r}

d1 <- d %>%
  select(Zufriedenheit_allgLeben, Person_persEinkommen) %>%
  group_by(Person_persEinkommen) %>%
  summarise(zMean = mean(Zufriedenheit_allgLeben, na.rm = T),
            zN = n(),
            zSD = sd(Zufriedenheit_allgLeben, na.rm = T)); d1

d2 <- d %>%
  select(Zufriedenheit_allgLeben, Person_persEinkommen) %>% 
  group_by(Zufriedenheit_allgLeben, Person_persEinkommen) %>% 
  tally(); d2

ggplot(d2, aes(x = Person_persEinkommen, y = Zufriedenheit_allgLeben)) + 
  geom_point(aes(size = n))





```




## Overall correlations

```{r}


d %>% glimpse()

d2 <- d %>% 
  select(Zufriedenheit_allgLeben, Person_Alter, Person_Aufenhaltssicherheit, 
         Person_BildAbschluss, Person_persEinkommen) %>% 
  mutate_all(as.integer); d2

cor1 <- cor(d2, use = "complete.obs", method = "spearman"); cor1

corrplot(corr = cor1, type = "upper", order = "hclust", method = "number",
         tl.col = "black", tl.srt = 45)

```




# Regression analysis

http://r-statistics.co/Linear-Regression.html

```{r}


d2 <- d %>% 
  select(Zufriedenheit_allgLeben, Person_Alter, Person_Gender, Person_Kinder,
         Person_Aufenhaltssicherheit, Person_Einzelhaushalt, 
         Person_BildAbschluss, Person_persEinkommen) %>% 
  mutate_all(as.integer); d2
d2 %>% glimpse()

lm1 <- lm(Zufriedenheit_allgLeben ~ 
            Person_Alter + 
            Person_Gender + 
            Person_Kinder + 
            Person_Einzelhaushalt +
            Person_Aufenhaltssicherheit + 
            Person_BildAbschluss + 
            Person_persEinkommen, 
          data = d2)
print(lm1)
summary(lm1)

```


























